---
title: "管道统计分析——rstatix使用指南"
author: "王诗翔"
date: "2019-07-07"
lastmod: "`r Sys.Date()`"
slug: ""
categories: [r]
tags: [r, stats]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, dev = "png", comment = "#>")
#Sys.setlocale('LC_ALL','C') # Embed this directly in the Rmarkdown script that contains the Chinese character comment
options(digits=3)
options(max.print=200)
```

原英文文档地址：<https://raw.githubusercontent.com/kassambara/rstatix/master/README.Rmd>

**rstatix** 包提供了一个与「tidyverse」设计哲学一致的简单且直观的管道友好框架用于执行基本的统计检验，
包括 t 检验、Wilcoxon 检验、ANOVA、Kruskal-Wallis 以及相关分析。

每个检验的输出都会自动转换为干净的数据框以便于可视化。

另外也提供了一些用于重塑、重排、操作以及可视化相关矩阵的函数。也包含一些方便因子实验分析的函数，包括
'within-Ss' 设计 (repeated measures), purely 'between-Ss' 设计以及 mixed 'within-and-between-Ss' 设计。
     
该包也可以用于计算一些效应值度量，包括 "eta squared" for ANOVA, "Cohen's d" for t-test and "Cramer's V" for the association between categorical variables。
该包还包含一些用于识别单变量和多变量离群点、评估变异正态性和异质性的帮助函数。   
   
## 核心函数
  
### 描述统计量
   
- `get_summary_stats()`: Compute summary statistics for one or multiple numeric variables. Can handle grouped data.
- `freq_table()`: Compute frequency table of categorical variables.
- `get_mode()`: Compute the mode of a vector, that is the most frequent values.
- `identify_outliers()`: Detect univariate outliers using boxplot methods. 
- `mahalanobis_distance()`: Compute Mahalanobis Distance and Flag Multivariate Outliers.
- `shapiro_test()` and `mshapiro_test()`: Univariate and multivariate Shapiro-Wilk normality test.
   
   
### 比较均值
     
- `t_test()`: perform one-sample, two-sample and pairwise t-tests
- `wilcox_test()`: perform one-sample, two-sample and pairwise Wilcoxon tests
- `sign_test()`: perform sign test to determine whether there is a median difference between paired or matched observations.
- `anova_test()`: an easy-to-use wrapper around `car::Anova()` to perform different types of ANOVA tests, including **independent measures ANOVA**, **repeated measures ANOVA** and **mixed ANOVA**.
- `kruskal_test()`: perform kruskal-wallis rank sum test
- `tukey_hsd()`: performs tukey post-hoc tests. Can handle different inputs formats: aov, lm, formula.
- `dunn_test()`: compute multiple pairwise comparisons following Kruskal-Wallis test.
- `emmeans_test()`: pipe-friendly wrapper arround `emmeans` function to perform pairwise comparisons of estimated marginal means. Useful for post-hoc analyses following up ANOVA/ANCOVA tests.
- `get_comparisons()`: Create a list of possible pairwise comparisons between groups.
- `get_pvalue_position`: autocompute p-value positions for plotting significance using ggplot2.
   
### 促进R的ANOVA计算
   
- `factorial_design()`: build factorial design for easily computing ANOVA using the `car::Anova()` function. This might be very useful for repeated measures ANOVA, which is hard to set up with the `car` package.
- `anova_summary()`: Create beautiful summary tables of ANOVA test results obtained from either `car::Anova()` or `stats::aov()`. The results include ANOVA table, generalized effect size and some assumption checks, such as Mauchly's test for sphericity in the case of repeated measures ANOVA.
   
### 比较方差
   
- `levene_test()`: Pipe-friendly framework to easily compute Levene's test for homogeneity of variance across groups. Handles grouped data.
- `box_m()`: Box's M-test for homogeneity of covariance matrices
   
   
### 效应值
   
- `cohens_d()`: Compute cohen's d measure of effect size for t-tests.
- `eta_squared()` and `partial_eta_squared()`: Compute effect size for ANOVA.
- `cramer_v()`: Compute Cramer's V, which measures the strength of the association between categorical variables.
   
### 相关分析
   
**计算相关性**:  
   
- `cor_test()`: correlation test between two or more variables using Pearson, Spearman or Kendall methods.
- `cor_mat()`: compute correlation matrix with p-values. Returns a data frame containing the matrix of the correlation coefficients. The output has an attribute named "pvalue", which contains the matrix of the correlation test p-values.
- `cor_get_pval()`: extract a correlation matrix p-values from an object of class `cor_mat()`.
- `cor_pmat()`: compute the correlation matrix, but returns only the p-values of the correlation tests.
- `as_cor_mat()`: convert a `cor_test` object into a correlation matrix format.
    
**重塑相关矩阵**:  
  
- `cor_reorder()`: reorder correlation matrix, according to the coefficients, using the hierarchical clustering method.
- `cor_gather()`: takes a correlation matrix and collapses (or melt) it into long format data frame (paired list)
- `cor_spread()`: spread a long correlation data frame into wide format (correlation matrix).
  
  
**取子集**:

- `cor_select()`: subset a correlation matrix by selecting variables of interest.
- `pull_triangle()`, `pull_upper_triangle()`, `pull_lower_triangle()`: pull upper and lower triangular parts of a (correlation) matrix.
- `replace_triangle()`, `replace_upper_triangle()`, `replace_lower_triangle()`: replace upper and lower triangular parts of a (correlation) matrix.
   
   
**可视化相关矩阵**:
   
- `cor_as_symbols()`: replaces the correlation coefficients, in a matrix, by symbols according to the value.
- `cor_plot()`: visualize correlation matrix using base plot.
- `cor_mark_significant()`: add significance levels to a correlation matrix.
  
  
### 矫正p值和添加显著性标记
      
- `adjust_pvalue()`: add an adjusted p-values column to a data frame containing statistical test p-values
- `add_significance()`: add a column containing the p-value significance level
   
   
### 其他
   
- `doo()`: alternative to dplyr::do for doing anything. Technically it uses `nest() + mutate() + map()` to apply arbitrary computation to a grouped data frame.
- `sample_n_by()`: sample n rows by group from a table
- `convert_as_factor(), set_ref_level(), reorder_levels()`: Provides pipe-friendly functions to convert simultaneously multiple variables into a factor variable.
- `make_clean_names()`: Pipe-friendly function to make syntactically valid column names (for input data frame) or names (for input vector).
   
   
## 安装和加载
    
    
- 从[GitHub](https://github.com/kassambara/rstatix)上安装开发版本：
    
   
```{r, eval = FALSE}
if(!require(devtools)) install.packages("devtools")
devtools::install_github("kassambara/rstatix")
```
     
     
- 或者从[CRAN](https://cran.r-project.org/package=ggpubr)安装稳定版本：
    
     
```{r, eval = FALSE}
install.packages("rstatix")
```


- 加载包
   
```{r}
library(rstatix)  
library(ggpubr)  # For easy data-visualization
```
  
  
## 描述统计量
    
```{r}
# Summary statistics of some selected variables
#::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
iris %>% 
  get_summary_stats(Sepal.Length, Sepal.Width, type = "common")

# Whole data frame
#::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
iris %>% get_summary_stats(type = "common")


# Grouped data
#::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
iris %>%
  group_by(Species) %>% 
  get_summary_stats(Sepal.Length, type = "mean_sd")
```

     
## 比较均值
   
你可以使用 `t_test()` (parametric) or `wilcox_test()` (non-parametric，实际比较的是中位数) 比较均值差异。下面使用 t 检验进行示范。
   
### 数据
   
导入样例数据集：
   
```{r}
df <- ToothGrowth
df$dose <- as.factor(df$dose)
head(df)
```

   
### 比较2个独立组别
   
   
- 创建一个带p值的箱线图
   
```{r unpaired-two-sample-t-test, fig.width=3.5, fig.height=4}
# T-test
stat.test <- df %>% 
  t_test(len ~ supp, paired = FALSE) 
stat.test

# Create a box plot
p <- ggboxplot(
  df, x = "supp", y = "len", 
  color = "supp", palette = "jco", ylim = c(0,40)
  )
# Add the p-value manually
p + stat_pvalue_manual(stat.test, label = "p", y.position = 35)
```
    
    
- 使用 [glue expression](https://github.com/tidyverse/glue) 自定义标签：

  
```{r custoize-p-value-labels, fig.width=3.5, fig.height=4}
p +stat_pvalue_manual(stat.test, label = "T-test, p = {p}", 
                      y.position = 36)
```
    
    

- 分组数据：在按照「dose」分组后比较 supp 水平：
   
```{r grouped-two-sample-t-test, fig.width=6, fig.height=4}
# Statistical test
stat.test <- df %>%
  group_by(dose) %>%
  t_test(len ~ supp) %>%
  adjust_pvalue() %>%
  add_significance("p.adj")
stat.test

# Visualization
ggboxplot(
  df, x = "supp", y = "len",
  color = "supp", palette = "jco", facet.by = "dose",
  ylim = c(0, 40)
  ) +
  stat_pvalue_manual(stat.test, label = "p.adj", y.position = 35)
```
   
   
### 比较配对样本
    
    
```{r paired-t-test, fig.width=3.5, fig.height=4}
# T-test
stat.test <- df %>% 
  t_test(len ~ supp, paired = TRUE) 
stat.test

# Box plot
p <- ggpaired(
  df, x = "supp", y = "len", color = "supp", palette = "jco", 
  line.color = "gray", line.size = 0.4, ylim = c(0, 40)
  )
p + stat_pvalue_manual(stat.test, label = "p", y.position = 36)
```
    
    
   
### 成对比较
   
   
- 成对比较：如果分组变量包含多于2个分类，会自动执行成对比较
   
   
```{r pairwise-comparisons, fig.width=3.5, fig.height=3}
# Pairwise t-test
pairwise.test <- df %>% t_test(len ~ dose)
pairwise.test
# Box plot
ggboxplot(df, x = "dose", y = "len")+
  stat_pvalue_manual(
    pairwise.test, label = "p.adj", 
    y.position = c(29, 35, 39)
    )
```
    
    
    
- 基于参考组的成对比较
    
    
```{r comaprison-against-reference-group, fig.width=3.5, fig.height=3}
# Comparison against reference group
#::::::::::::::::::::::::::::::::::::::::
# T-test: each level is compared to the ref group
stat.test <- df %>% t_test(len ~ dose, ref.group = "0.5")
stat.test
# Box plot
ggboxplot(df, x = "dose", y = "len", ylim = c(0, 40)) +
  stat_pvalue_manual(
    stat.test, label = "p.adj.signif", 
    y.position = c(29, 35)
    )
# Remove bracket
ggboxplot(df, x = "dose", y = "len", ylim = c(0, 40)) +
  stat_pvalue_manual(
    stat.test, label = "p.adj.signif", 
    y.position = c(29, 35),
    remove.bracket = TRUE
    )
```
   
   
- 基于总体水平的成对比较
   
   
```{r comparison-against-base-mean, fig.width=3.5, fig.height=3}
# T-test
stat.test <- df %>% t_test(len ~ dose, ref.group = "all")
stat.test
# Box plot with horizontal mean line
ggboxplot(df, x = "dose", y = "len") +
  stat_pvalue_manual(
    stat.test, label = "p.adj.signif", 
    y.position = 35,
    remove.bracket = TRUE
    ) +
  geom_hline(yintercept = mean(df$len), linetype = 2)
```
    
    
## ANOVA 检验
    
```{r}
# One-way ANOVA test
#:::::::::::::::::::::::::::::::::::::::::
df %>% anova_test(len ~ dose)

# Two-way ANOVA test
#:::::::::::::::::::::::::::::::::::::::::
df %>% anova_test(len ~ supp*dose)

# Two-way repeated measures ANOVA
#:::::::::::::::::::::::::::::::::::::::::
df$id <- rep(1:10, 6) # Add individuals id
# Use formula
# df %>% anova_test(len ~ supp*dose + Error(id/(supp*dose)))
# or use character vector
df %>% anova_test(dv = len, wid = id, within = c(supp, dose))

# Use model as arguments
#:::::::::::::::::::::::::::::::::::::::::
.my.model <- lm(yield ~ block + N*P*K, npk)
anova_test(.my.model)
```
   
   
## 相关检验
   
```{r}
# Data preparation
mydata <- mtcars %>% 
  select(mpg, disp, hp, drat, wt, qsec)
head(mydata, 3)

# Correlation test between two variables
mydata %>% cor_test(wt, mpg, method = "pearson")

# Correlation of one variable against all
mydata %>% cor_test(mpg, method = "pearson")

# Pairwise correlation test between all variables
mydata %>% cor_test(method = "pearson")
```
   
   
## 相关矩阵
   
```{r, fig.width=4, fig.height=4}
# Compute correlation matrix
#::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
cor.mat <- mydata %>% cor_mat()
cor.mat

# Show the significance levels
#::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
cor.mat %>% cor_get_pval()

# Replacing correlation coefficients by symbols
#::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
cor.mat %>%
  cor_as_symbols() %>%
  pull_lower_triangle()

# Mark significant correlations
#::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
cor.mat %>%
  cor_mark_significant()


# Draw correlogram using R base plot
#::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
cor.mat %>%
  cor_reorder() %>%
  pull_lower_triangle() %>% 
  cor_plot()
```

    
## 相关文章
   
   
- [在ggplot上添加p值和显著性水平](http://www.sthda.com/english/articles/24-ggpubr-publication-ready-plots/76-add-p-values-and-significance-levels-to-ggplots/)
