---
title: "Rprofile：R 全局设置"
author: "王诗翔"
date: "2020-08-13"
lastmod: "`r Sys.Date()`"
slug: ""
categories: ["r", "config"]
tags: ["r", "config", ".Rprofile"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, dev = "png", comment = "#>", tidy = "styler")
#Sys.setenv("LANGUAGE"="EN") # Embed this for outputing English message
#Sys.setlocale('LC_ALL','C') # Embed this directly in the Rmarkdown script that contains the Chinese character comment
options(digits=3)
options(max.print=200)
```

存储在 `~/.Rprofile` 中的内容是一个 R 脚本，它会在 R 启动时自动运行，所以可以作为全局的配置使用。

根据我的 R 使用经验，结合 Y 叔和 Yihui 提供的一些便利函数，我构建了一个比较合适的 R 配置。推荐大家结合自己需求使用和自定义。

目前设定涉及的功能：

1. 设置 `UTF-8` 编码。
2. 设置 R 提示用英文显示，方便查看和搜索 R 代码错误信息。
3. 设置 CRAN 下载源为同济大学；Bioconductor 下载源为清华大学。
4. 设定自定义 R 包存储路径，这个非常有用，便于以后 R 版本涉及不影响 R 包。
5. 设置 R 临时文件目录，这个在一些场景下也有用（比如快速查看临时文件）。
6. 设置载入 pacman 用来管理 R 包。
7. 设置 VSCode r 插件需要进行的设置。
8. 提供一些工具函数，目前主要来自 Y 叔的 rvcheck 包和 Yihui 的 xfun 包。

**该脚本配置我会长期维护**。如果大家有问题或建议、增加新的工具函数，欢迎通过邮件或 <https://github.com/ShixiangWang/MessageBoard/issues> 进行反馈和交流。

```{r, eval=FALSE}
#------------------------------------------------------------
#                  |R Global Setting|
#
# You can (un)comment any code you dislike.
#   Any Question, please email to
#       Shixiang Wang <w_shixiang@163.com>
#   or file an issue to
#       <https://github.com/ShixiangWang/MessageBoard/issues>
#------------------------------------------------------------


# Global options ----------------------------------------------------------
options(encoding = "UTF-8") # Set file encoding
Sys.setenv("LANGUAGE" = "EN") # Set language of R message

# Package download mirrors ------------------------------------------------
## For Bioconductor packages
options(BioC_mirror = "https://mirrors.tuna.tsinghua.edu.cn/bioconductor")
## For CRAN packages
## Full list see mirrors on <https://cran.r-project.org/>
options("repos" = c(CRAN = "https://mirrors.tongji.edu.cn/CRAN/"))

# Set local custom R library path -----------------------------------------
.CUSTOM_LIB <- "~/Library/R" # Set your custom library location
# Please do not add '/' at the end !!!

if (!dir.exists(.CUSTOM_LIB)) {
  dir.create(.CUSTOM_LIB, recursive = TRUE)
}

.libPaths(c(.CUSTOM_LIB, .libPaths()))
message("Using library: ", .libPaths()[1])

# Set R temp directory ----------------------------------------------------
## Uncomment the following code if you want to set R temp directory
# .TMP = "~/Rtmp"
# if(dirname(tempdir()) != .TMP){
#   if(!dir.exists(.TMP)) dir.create(.TMP)
#   cat(paste0("TMPDIR = ", .TMP), file="~/.Renviron", sep = "\n")
# }
# message("Using temp directory: ", .TMP)


# Use pacman to manage R packages -----------------------------------------
# Reference: <https://www.jianshu.com/p/cb16ded75672>
if (!requireNamespace("pacman", quietly = TRUE)) {
  install.packages("pacman", dependencies = TRUE)
}

library(pacman)

## Packages to load when R starts
pacman::p_load(roxytest)  # For writing tests in .R comments

# VSCode plugin setting ---------------------------------------------------
# Only use when you code R with VSCode
# Reference: <https://github.com/REditorSupport/vscode-r-lsp>
if (!requireNamespace("languageserver", quietly = TRUE)) {
  pacman::p_install(languageserver)
}

source(file.path(
  if (.Platform$OS.type == "windows") {
    file.path(Sys.getenv("HOMEDRIVE"), Sys.getenv("HOMEPATH"))
  } else {
    Sys.getenv("HOME")
  }, ".vscode-R", "init.R"
))

## Set format style
options(languageserver.formatting_style = function(options) {
  style <- styler::tidyverse_style(indent_by = options$tabSize)
  style$token$force_assignment_op <- NULL  # Not force modifying '=' to '<-'
  style
})

# Global utilities --------------------------------------------------------

## Try installing R packages again and again
## It may be useful when install GitHub R packages
.loop_install <- function(pkgs, force = FALSE) {
  ## If force=TRUE,
  ## force installation when packages already exist on local system.
  Sys.sleep(1)
  tryCatch(
    {
      message("=> Try installing ", paste(pkgs, collapse = ", "))
      gh_pkg <- pkgs[grepl("/", pkgs)]
      ot_pkg <- setdiff(pkgs, gh_pkg)
      if (length(ot_pkg) > 0) {
        pacman::p_install(ot_pkg, character.only = TRUE, force = force)
      } else {
        if (!requireNamespace("remotes", quietly = TRUE)) {
          pacman::p_install(remotes)
        }
        remotes::install_github(gh_pkg, force = force)
      }
    },
    error = function(e) {
      .loop_install(pkgs, force)
    }
  )
}

## Utilities from rvcheck, xfun and other R package
## Thanks to the authors
if (!requireNamespace("rvcheck", quietly = TRUE)) {
  pacman::p_install(rvcheck)
}
if (!requireNamespace("xfun", quietly = TRUE)) {
  pacman::p_install(xfun)
}

## Load function from package
.get_fun <- function(pkg, fun) {
  get(fun,
      envir = asNamespace(pkg),
      inherits = FALSE
  )
}
## Open any directory in any operating system
.open <- rvcheck::o
## Check whether packages were installed
.is_installed <- rvcheck::is.installed
## Check if on a R server
.is_rserver <- suppressMessages(.get_fun("rvcheck", "is.rserver"))
## Simpler function to download file
.download_file <- xfun::download_file
.upload_ftp <- xfun::upload_ftp
## Functions to obtain, remove, and change extensions in filenames
.fl_ext <- xfun::file_ext
.rm_ext <- xfun::sans_ext
.ch_ext <- xfun::with_ext
## Provide the "file" version of gsub(),
## i.e., they perform searching and replacement in files via gsub().
.gsub_file <- xfun::gsub_file
.gsub_files <- xfun::gsub_files
.gsub_dir <- xfun::gsub_dir
.gsub_ext <- xfun::gsub_ext
## Change the working directory, evaluate the expression,
## and restore the working directory
.move_run <- xfun::in_dir
## Install a source package from a directory
.install_dir <- xfun::install_dir
## Check OS
.is_linux <- xfun::is_linux
.is_windows <- xfun::is_windows
.is_macos <- xfun::is_macos
.is_unix <- xfun::is_unix
## Number to words, e.g. 1 to one, 10 to ten
.numbers_to_words <- xfun::numbers_to_words
## Read or write files, assuming they are encoded in UTF-8.
.read_file <- xfun::read_utf8
.write_file <- xfun::write_utf8
```
