---
title: "contribution - A Tiny Contribution Table Generator Based on ggplot2"
author: "王诗翔"
date: "2019-07-13"
lastmod: "`r Sys.Date()`"
slug: ""
categories: [r]
tags: [r, package, contribution]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, dev = "png", comment = "#>")
#Sys.setlocale('LC_ALL','C') # Embed this directly in the Rmarkdown script that contains the Chinese character comment
options(digits=3)
options(max.print=200)
```

The goal of **contribution** is to generate **contribution table** for credit assignment in a project. 
This is inspired by Nick Steinmetz (see twitter <https://twitter.com/SteinmetzNeuro/status/1147241138291527681>). 

> Authors contributions sections are new and still don’t appear in major journals, but can be improved. Rather than text listing each author’s contributions, the same data can be presented as a table with rows corresponding to contributions and columns for each author.
>
> Advantages include: 
>
> 1. Graphics are faster and easier to comprehend. They are also easier to locate in the document.
>
> 2. This format can be readily augmented with additional information, such as distinguishing between ‘major’ and ‘minor’ contributions of each type.
>
> 3. This format can be read as easily in either direction, answering both "Who did X?" and "What did person Y do?" equally. 
>
> 4. This format lends itself to a nice extension for including your author contribution information on your CV: a similar table where each column is one of your papers.
>
>
> A difficulty with this is the diversity of terminology used, which would be helped by refinement and more widespread adoption of the CRediT framework (https://www.casrai.org/credit.html ). 

## Table of Contents

* [Feature](#feature)
* [Installation](#Installation)
* [Basic example](#basic-example)
* [GitHub contribution](#gitHub-contribution)
* [Palette](#palette)
* [CRediT](#credit)
* [More about GitHub stats](#more-about-github-stats)

## Feature

* Support table type
  * 3-level contribution (i.e. 'None', 'Minor' and 'Major')
  * numeric contribution
* Pull commit number and code lines from GitHub
* Dataset `palette` contains 27 color maps


## Installation

You can install the released version of contribution from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("contribution")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("openbiox/contribution")
```

## Basic example

This is a basic example which shows you how to plot a simple contribution table:

```{r example}
library(contribution)
data("demo")
demo
```

The accepted data format is a `data.frame` whose first column show the `role` and the other 
columns show the people or projects. This format is easy to create using R or other tools like Excel. 

For a 3-level contribution table, only `Minor` and `Major` are valid, a `NA` value should put 
in cell for no contribution.

```{r, fig.height=3}
generate(demo)
```

The **white** box represents **no contribution**, the **grey** box represents **minor contribution**, 
and the **black** box represents **major contribution**.

The table is nice, easy to read. The result is a `ggplot` object, so you can modify in your way!

You can also use other colors and `scale_fill_*` function from **ggplot2** to map colors:

```{r, fig.height=3}
library(ggplot2)
generate(demo, text_angle_x = 20, color_map = scale_fill_brewer(palette ="Oranges"))
```

When it is not easy to see the meaning of color, you can show the legend.

```{r, fig.height=3}
generate(demo, text_angle_x = 20, color_map = scale_fill_brewer(palette ="Set1"), show_legend = TRUE)
```


## GitHub contribution

To show how to generate numeric contribution table, here we use commit number of GitHub project as 
an example.

To get data from GitHub, I created a function `pull_github()`.

```{r}
# Github project contributions
my_contr = dplyr::tibble(
           repo = c("UCSCXenaTools", "maftools"),
           owner = c("ShixiangWang", "PoisonAlien"),
           username = "ShixiangWang",
           role = c("Developer", "Contributor"))
my_contr
contr_tb = pull_github(data = my_contr)
contr_tb
```

Now we have data format the `generate()` function can accept, show the plot!


```{r}
generate(contr_tb, show_legend = TRUE, hjust_x = 0)
```

## Palette

To change colors of contribution graph, I generated a dataset `palette` 
according to themes provided by project [github-contribution-color-graph](https://github.com/williambelle/github-contribution-color-graph).

We can show the palette and choose the color we like.

```{r, results="hide"}
show_palette()
```

Just put the name to option `palette_name`.

```{r}
generate(contr_tb, show_legend = TRUE, hjust_x = 0,
         palette_name = "psychedelic")
generate(contr_tb, show_legend = TRUE, hjust_x = 0,
         palette_name = "cyan")
```


More custom options please run `?generate` in R console.


## CRediT

**CRediT** can help assign the role, this data has been stored in this package.

```{r}
data("CRediT")
```

Show whole table.

```{r}
knitr::kable(CRediT, format = "html")
```

## More about GitHub stats

**contribution** package supports the following GitHub stats:

* commit number contributed to a repo
* number of code line contributed a repo
  * all
  * addition
  * deletion
  

Firstly define our targets.  

```{r}
library(contribution)

my_contr = dplyr::tibble(
           repo = c("UCSCXenaTools", "XenaShiny", "metawho", 
                    "maftools", "DoAbsolute", "contribution"),
           owner = c("ropensci", "openbiox", "ShixiangWang",
                     "PoisonAlien", "ShixiangWang", "openbiox"),
           username = "ShixiangWang",
           role = c("Developer", "Project leader", "Developer",
                    "Contributor", "Developer", "Developer"))
my_contr
```


### Commit number

At default, `pull_github()` function will pull commit number from GitHub API.

```{r}
contr_tb = pull_github(data = my_contr)
contr_tb
```


```{r}
generate(contr_tb, show_legend = TRUE, hjust_x = 0,
         palette_name = "indigo", text_angle_x = 60)
```

### Number of code line

If we want to get number of code line, we can set the `type` option.

```{r}
# Total number
contr_tb1 = pull_github(data = my_contr, report_lines = T,  type = 'all')
contr_tb1

# Number of additions
contr_tb2 = pull_github(data = my_contr, report_lines = T, type = 'add')
contr_tb2

# Number of deletions
contr_tb3 = pull_github(data = my_contr, report_lines = T, type = 'del')
contr_tb3
```


```{r}
generate(contr_tb1, show_legend = TRUE, hjust_x = 0,
         palette_name = "pink", text_angle_x = 60)
generate(contr_tb2, show_legend = TRUE, hjust_x = 0,
         palette_name = "teal", text_angle_x = 60)
generate(contr_tb3, show_legend = TRUE, hjust_x = 0,
         palette_name = "summer", text_angle_x = 60)
```

### GitHub limit and token management

For unauthenticated requests, the rate limit allows for up to 60 requests per hour. For API requests using Basic Authentication or OAuth, you can make up to 5000 requests per hour. Here we use token to manage this. Obtain a personal access token (PAT) from here: https://github.com/settings/tokens.

You can see how many times you left with `pull_github_limit()` function.

```{r}
pull_github_limit()
```

Typically, you can set token to `GITHUB_PAT` variable in your `.Renviron` file using the following format:

```
GITHUB_PAT=8c70fd8419398999c9ac5bacf3192882193cadf2
```

You can also set it in your `.Rprofile` file using the following format:

```
Sys.setenv(GITHUB_PAT="8c70fd8419398999c9ac5bacf3192882193cadf2")
```
